### 2022-02-17 appendix_kronecker/appendix.tex
first draft of the whole thing! :D

A property of the Kronecker sum is 
\begin{align}\label{eqn:kron exp}
	e^{\bs A\oplus \bs{B}}= e^{\bs A}\otimes e^{\bs{B}}.
\end{align}
\begin{proof}
	First, the matrices \(\bs A\otimes \bs{I}_m\) and \(\bs{I}_n\otimes \bs{B}\) commute; from the mixed product rule their product is \(\bs A\otimes \bs{B}\). Hence 
	\[e^{\bs A\oplus \bs{B}} = e^{\bs A\otimes \bs{I}_m}e^{\bs{I}_n\otimes \bs{B}}.\]
	We now show that \(e^{\bs A\otimes \bs{I}_m} = e^{\bs A}\otimes \bs{I}_m\) and \(e^{\bs{I}_n\otimes \bs{B}}=\bs{I}_n\otimes e^{\bs{B}}\). The latter follows from the fact that \(\bs{I}_n\otimes \bs{B}\) is a block diagonal matrix with blocks \(\bs{B}\), hence its exponential is also block diagonal with blocks equal to the exponential of \(\bs{B}\). The former follows from 
	\begin{align}
	e^{\bs A\otimes \bs{I}_m} &= \sum_{n=0}^\infty \cfrac{1}{n!}\left(\bs A\otimes \bs{I}_m\right)^n \nonumber
	\\&= \sum_{n=0}^\infty \cfrac{1}{n!}\left(\bs A^n\otimes \bs{I}_m\right) \nonumber
	\\&=\left(\sum_{n=0}^\infty \cfrac{1}{n!}\bs A\otimes \bs{I}_m\right) \nonumber
	\\&=e^{\bs A}\otimes \bs{I}_m.\label{eqn:09ksdjgah}
	\end{align}

@@

\begin{lem}\label{lem: lst mpr}
	Let \(\bs{T}\) and \(\bs{C}\) be \(n\times n\), square matrices with \(\bs{C}\) diagonal and invertible; let \(\bs{S}\) be a \(p\times p\) matrix. Further, suppose \(\left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]\) is invertible for \(\lambda>0\). Then
\begin{align}
	&\int_{t=0}^\infty e^{-\lambda t}  e^{{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t}} \wrt t 
	%
	=   \int_{x=0}^\infty e^{{\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)x}}\otimes e^{\bs{S}x} \wrt x \left(\bs{C}\otimes \bs{I}\right)^{-1}.  \label{eqn:lstsimplify}\end{align}
\end{lem}
\begin{proof}
	Computing the integral on the left-hand side and then factorising the result and using the \ref{eqn:mpr} multiple times gives
	\begin{align}
            	\int_{t=0}^\infty e^{-\lambda t} e^{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t} \wrt t\nonumber 
            	%
            	&= - \left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]^{-1}
		%
		\\&= -  \left[\bs{T}\otimes \bs{I} + \left(\bs{C}\otimes \bs{I}\right)\left(\bs{I}\otimes \bs{S}\right) - \lambda \bs{I}\right]^{-1}\nonumber
		%
		\\&= -  \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}\otimes \bs{I}\right)^{-1}\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}\otimes \bs{I}\right)^{-1}\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 12}
		%
	\end{align}
	By Equation~(\ref{eqn:kron inverse}) and since \(\bs{C}\) is invertible, (\ref{eqn: ref this one 12}) is equal to
	\begin{align}
		& - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\otimes \bs{I}\right)\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\otimes \bs{I}\right)\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 13}
		%
	\end{align}
	{Using the \ref{eqn:mpr} and algebraic manipulation, (\ref{eqn: ref this one 13}) is equal to }
	\begin{align}
		&- \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\bs{T}\right)\otimes \bs{I} + \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\lambda \bs{I}\right)\otimes \bs{I}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1} \nonumber
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\oplus \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1},\label{eqn: is an integral}
	\end{align}
	by definition of the Kronecker sum.

	Now, for an invertible matrix \(\bs A\) we can write \(-\bs A^{-1} = \displaystyle\int_{x=0}^\infty e^{\bs Ax}\wrt x\). Therefore (\ref{eqn: is an integral}) is 
	\begin{align*}
		-\left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\oplus \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1}
		&= \int_{x=0}^\infty e^{\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)x\right)\oplus \bs{S}x}\wrt x\left(\bs{C}\otimes \bs{I}\right)^{-1}.
	\end{align*}
	{Using the rule in Equation~(\ref{eqn:kron exp}) gives }
	\begin{align*}
		&\int_{x=0}^\infty e^{\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)x}\otimes e^{ \bs{S}x}\wrt x\left(\bs{C}\otimes \bs{I}\right)^{-1},
	\end{align*}
	which is the result.
\end{proof}

@@

Let \(\bs H_{12}(t)\) be the top-right quadrant of \(e^{\bs Bt}\) of size \(m_1\times m_2\), i.e.
\begin{align}
	\bs H_{12}(t) &= \vligne{  \bs I_{m_1\times m_1} & \bs 0}e^{\bs Bt} \left[\begin{array}{c} \bs 0 \\ \bs I_{m_2\times m_2}\end{array}\right]. \label{eqn: p03j}
\end{align}
Denote by \(\widehat{\bs H}_{11}(\lambda):=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{11}(t)\wrt t\) and by \(\widehat{\bs H}_{12}(\lambda):=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{12}(t)\wrt t\), the Laplace transforms of \(\bs H_{11}(t)\) and \(\bs H_{12}(t)\), respectively. Using Lemma~\ref{lem: sfkjgn} we can show the following result. 
\begin{lem}
	\begin{align}
		\widehat{\bs H}_{11}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \wrt x,\label{eqn: 202}
		%
		\\\widehat{\bs H}_{12}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\wrt x.\label{eqn: 203}
	\end{align}
\end{lem}
\begin{proof}
	First we show the result for \(\widehat{\bs H}_{11}(\lambda)\). Taking the Laplace transform of (\ref{eqn: akg987LKJ}) shows that \(\widehat{\bs H}_{11}(\lambda)\) is equal to 
	\begin{align}
		&\int_{t=0}^\infty \int_{v=0}^t\int_{u=v}^t e^{-\lambda (t-u)}e^{\bs B_{11}(t-u)}\bs B_{12}e^{-\lambda (u-v)}e^{\bs B_{22}(u-v)}\bs B_{21}e^{-\lambda v}\bs H_{11}(v)\wrt u\wrt v \nonumber 
		\\&\qquad{}+ (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\nonumber 
		%
		\\& = (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1} + (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\widehat{\bs H}_{11}(\lambda),
	\end{align}
	by the convolution theorem for Laplace transforms. This implies
	\begin{align*}
		&\left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]\widehat{\bs H}_{11}(\lambda) 
		\\&= (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1},
	\end{align*}
	and therefore 
	\begin{align*}
		&\widehat{\bs H}_{11}(\lambda) 
		\\&= \left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1} (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}
		%
		\\&= \left[(\lambda \bs I_{m_1\times m_1} - \bs B_{11})\left(\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)\right]^{-1} 
		%
		\\&= \left[\lambda \bs I_{m_1\times m_1} - \bs B_{11} - \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1}
		%
		\\&= \int_{t=0}^\infty e^{\left(\bs B_{11} - \lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)t}\wrt t,
	\end{align*}
	which is (\ref{eqn: 202}).

@@

Now, recall the matrix-functions
\begin{align*}
	% \bs Q_{+0}(\lambda) &= \bs C_+^{-1}\bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1},
	% %
	% \\\bs Q_{-0}(\lambda) &= \bs C_-^{-1}\bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1},
	%
	\bs Q_{++}(\lambda) &= \bs C_+^{-1} \left(\bs T_{++} - \lambda \bs I + \bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0+}\right),
	%
	\\\bs Q_{+-}(\lambda) &= \bs C_+^{-1} \left(\bs T_{+-} + \bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0-} \right) ,
	%
	\\\bs Q_{--}(\lambda) &= \bs C_-^{-1} \left(\bs T_{--}  - \lambda \bs I + \bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0-}\right),
	%
	\\\bs Q_{-+}(\lambda) &=\bs C_-^{-1} \left(\bs T_{-+}+ \bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0+}\right) ,
\end{align*}
from Chapter~\ref{sec: conv}.
\begin{cor}\label{cor: mpr B}
	For \(m\in\{+,-\}\) the top-left quadrant of size \(m_1\times m_1=|\calS_m|\cdot p \times |\calS_m|\cdot p\) of \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I & \bs 0}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t\left[\begin{array}{c} \bs I \\ \bs 0 \end{array}\right], \nonumber
	\end{align}
	is given by 
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm} (\lambda)x}\otimes  e^{\bs S x}\wrt x(\bs C_m^{-1}\otimes \bs I).\label{eqn: skagh87} 
	\end{align}
	For \(m\in\{+,-\}\) the top-right quadrant of size \(m_1\times m_2=|\calS_m|\cdot p\times |\calS_0|\cdot p\) of  \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I & \bs 0}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t \left[\begin{array}{c}\bs 0 \\ \bs I\end{array}\right] ,\nonumber
	\end{align}
	is given by
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x((\bs C_m^{-1}\bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1})\otimes \bs I).\label{eqn: skagh873} 
	\end{align}
	Also, 
	\begin{align}
		&\vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t \bs{B}_{m{n}} %= \vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t  \left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
	= \int_{x=0}^\infty \bs H^{mn}(\lambda,x)  \otimes  e^{\bs S x}\bs D\wrt x\left(\vligne{\bs I_{pn} & \bs 0_{pn\times p|\calS_0|}}\right), \label{eqn: akgj987adKLDJ}
\end{align}
for \(m,n\in\{+,-\}\), \(m\neq n\).
\end{cor}
\begin{proof}
	From Lemma~\ref{lem: sfkjgn} the top-left quadrant of size \(m_1\times m_1=|\calS_m|\cdot p \times |\calS_m|\cdot p\) of the integral with respect to \(t\) on the left-hand side of (\ref{eqn: skagh87}) is 
	\begin{align}
		\int_{t=0}^\infty e^{\left(\bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S - \lambda \bs I+ (\bs T_{m0}\otimes \bs I)(\lambda \bs I-\bs T_{00}\otimes \bs I)^{-1}(\bs T_{0m}\otimes \bs I)\right)t}\wrt t. \label{eqn: akjf768}
	\end{align}
	By Lemma~\ref{lem: lst mpr}, (\ref{eqn: akjf768}) is equal to 
	\begin{align}
		&\int_{x=0}^\infty e^{\bs C_m^{-1}\left(\bs T_{mm} - \lambda \bs I+ \bs T_{m0} (\lambda \bs I-\bs T_{00})^{-1}\bs T_{0m} \right)x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1}\nonumber
		%
		\\&=\int_{x=0}^\infty e^{\bs Q_{mm} ( \lambda )x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1} , \label{eqn: akjf7623988}
	\end{align}
	from the definition of \(\bs Q_{mm}(\lambda)\). This proves (\ref{eqn: skagh87}).

>>>>

A property of the Kronecker sum is 
\begin{align}\label{eqn:kron exp}
	e^{\bs A\oplus \bs{B}}= e^{\bs A}\otimes e^{\bs{B}}.
\end{align}
\begin{proof}
	First, the matrices \(\bs A\otimes \bs{I}_m\) and \(\bs{I}_n\otimes \bs{B}\) commute; from the mixed product rule their product is \(\bs A\otimes \bs{B}\). Hence, 
	\[e^{\bs A\oplus \bs{B}} = e^{\bs A\otimes \bs{I}_m}e^{\bs{I}_n\otimes \bs{B}}.\]
	We now show that \(e^{\bs A\otimes \bs{I}_m} = e^{\bs A}\otimes \bs{I}_m\) and \(e^{\bs{I}_n\otimes \bs{B}}=\bs{I}_n\otimes e^{\bs{B}}\). The latter follows from the fact that \(\bs{I}_n\otimes \bs{B}\) is a block diagonal matrix with blocks \(\bs{B}\), hence its exponential is also block diagonal with blocks equal to the exponential of \(\bs{B}\). The former follows from 
	\begin{align}
	e^{\bs A\otimes \bs{I}_m} &= \sum_{n=0}^\infty \cfrac{1}{n!}\left(\bs A\otimes \bs{I}_m\right)^n \nonumber
	\\&= \sum_{n=0}^\infty \cfrac{1}{n!}\left(\bs A^n\otimes \bs{I}_m\right) \nonumber
	\\&=\left(\sum_{n=0}^\infty \cfrac{1}{n!}\bs A^n\otimes \bs{I}_m\right) \nonumber
	\\&=e^{\bs A}\otimes \bs{I}_m.\label{eqn:09ksdjgah}
	\end{align}

@@

\begin{lem}\label{lem: lst mpr}
	Let \(\bs{T}\) and \(\bs{C}\) be \(n\times n\), square matrices with \(\bs{C}\) diagonal and invertible; let \(\bs{S}\) be a \(p\times p\) matrix. Further, suppose \(\left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]\) is invertible for \(\lambda>0\). Then
\begin{align}
	&\int_{t=0}^\infty e^{-\lambda t}  e^{{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t}} \wrt t 
	%
	=   \int_{x=0}^\infty e^{{\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)x}}\otimes e^{\bs{S}x} \wrt x \left(\bs{C}\otimes \bs{I}\right)^{-1}.  \label{eqn:lstsimplify}\end{align}
\end{lem}
\begin{proof}
	Computing the integral on the left-hand side and then factorising the result and using the~\ref{eqn:mpr} multiple times gives
	\begin{align}
            	\int_{t=0}^\infty e^{-\lambda t} e^{\left(\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S}\right)t} \wrt t\nonumber 
            	%
            	&= - \left[\bs{T}\otimes \bs{I} + \bs{C}\otimes \bs{S} - \lambda \bs{I}\right]^{-1}
		%
		\\&= -  \left[\bs{T}\otimes \bs{I} + \left(\bs{C}\otimes \bs{I}\right)\left(\bs{I}\otimes \bs{S}\right) - \lambda \bs{I}\right]^{-1}\nonumber
		%
		\\&= -  \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}\otimes \bs{I}\right)^{-1}\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}\otimes \bs{I}\right)^{-1}\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 12}
		%
	\end{align}
	By Equation~(\ref{eqn:kron inverse}) and since \(\bs{C}\) is invertible, (\ref{eqn: ref this one 12}) is equal to
	\begin{align}
		& - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\otimes \bs{I}\right)\left(\bs{T}\otimes \bs{I} \right)+ \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\otimes \bs{I}\right)\lambda \bs{I}\right)\right]^{-1}. \label{eqn: ref this one 13}
		%
	\end{align}
	{Using the~\ref{eqn:mpr} and algebraic manipulation, (\ref{eqn: ref this one 13}) is equal to }
	\begin{align}
		&- \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\bs{T}\right)\otimes \bs{I} + \bs{I}\otimes \bs{S} - \left(\bs{C}^{-1}\lambda \bs{I}\right)\otimes \bs{I}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}\otimes \bs{I}\right)\left(\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right)\right]^{-1} \nonumber
		%
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\otimes \bs{I} + \bs{I}\otimes \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1} \nonumber
		\\&= - \left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\oplus \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1},\label{eqn: is an integral}
	\end{align}
	by definition of the Kronecker sum.

	Now, for an invertible matrix \(\bs A\) we can write \(-\bs A^{-1} = \displaystyle\int_{x=0}^\infty e^{\bs Ax}\wrt x\). Therefore, (\ref{eqn: is an integral}) is 
	\begin{align*}
		-\left[\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)\oplus \bs{S}\right]^{-1}\left(\bs{C}\otimes \bs{I}\right)^{-1}
		&= \int_{x=0}^\infty e^{\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)x\right)\oplus \bs{S}x}\wrt x\left(\bs{C}\otimes \bs{I}\right)^{-1}.
	\end{align*}
	{Using the rule in Equation~(\ref{eqn:kron exp}) gives }
	\begin{align*}
		&\int_{x=0}^\infty e^{\left(\bs{C}^{-1}\left(\bs{T}-\lambda \bs{I}\right)\right)x}\otimes e^{ \bs{S}x}\wrt x\left(\bs{C}\otimes \bs{I}\right)^{-1},
	\end{align*}
	which is the result.
\end{proof}

@@

Let \(\bs H_{12}(t)\) be the top-right quadrant of \(e^{\bs Bt}\) of size \(m_1\times m_2\), i.e.
\begin{align}
	\bs H_{12}(t) &= \vligne{  \bs I_{m_1\times m_1} & \bs 0}e^{\bs Bt} \left[\begin{array}{c} \bs 0 \\ \bs I_{m_2\times m_2}\end{array}\right]. \label{eqn: p03j}
\end{align}
Denote by \(\widehat{\bs H}_{11}(\lambda):=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{11}(t)\wrt t\) and by \(\widehat{\bs H}_{12}(\lambda):=\displaystyle \int_{t=0}^\infty e^{-\lambda t}\bs H_{12}(t)\wrt t\), the Laplace transforms of \(\bs H_{11}(t)\) and \(\bs H_{12}(t)\), respectively. Using Lemma~\ref{lem: sfkjgn} we can show the following result. 
\begin{lem} Assuming \(\lambda >0\) and \(\lambda\bs I-\bs B_{22}\) is invertible, then 
	\begin{align}
		\widehat{\bs H}_{11}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \wrt x,\label{eqn: 202}
		%
		\\\widehat{\bs H}_{12}(\lambda) &= \int_{x=0}^\infty e^{\left(\bs B_{11} -\lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}- \bs B_{22})^{-1}\bs B_{21}\right)x} \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\wrt x.\label{eqn: 203}
	\end{align}
\end{lem}
\begin{proof}
	First we show the result for \(\widehat{\bs H}_{11}(\lambda)\). Taking the Laplace transform of (\ref{eqn: akg987LKJ}) shows that \(\widehat{\bs H}_{11}(\lambda)\) is equal to 
	\begin{align}
		&\int_{t=0}^\infty \int_{v=0}^t\int_{u=v}^t e^{-\lambda (t-u)}e^{\bs B_{11}(t-u)}\bs B_{12}e^{-\lambda (u-v)}e^{\bs B_{22}(u-v)}\bs B_{21}e^{-\lambda v}\bs H_{11}(v)\wrt u\wrt v \nonumber 
		\\&\qquad{}+ (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\nonumber 
		%
		\\& = (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1} + (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\widehat{\bs H}_{11}(\lambda),
	\end{align}
	by the convolution theorem for Laplace transforms. This implies
	\begin{align*}
		&\left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]\widehat{\bs H}_{11}(\lambda) 
		\\&= (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1},
	\end{align*}
	and therefore 
	\begin{align*}
		&\widehat{\bs H}_{11}(\lambda) 
		\\&= \left[\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1} (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}
		%
		\\&= \left[(\lambda \bs I_{m_1\times m_1} - \bs B_{11})\left(\bs I_{m_1\times m_1} -  (\lambda \bs I_{m_1\times m_1} - \bs B_{11})^{-1}\bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)\right]^{-1} 
		%
		\\&= \left[\lambda \bs I_{m_1\times m_1} - \bs B_{11} - \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right]^{-1}
		%
		\\&= \int_{t=0}^\infty e^{\left(\bs B_{11} - \lambda \bs I_{m_1\times m_1} + \bs B_{12}(\lambda \bs I_{m_2\times m_2}-\bs B_{22})^{-1}\bs B_{21}\right)t}\wrt t,
	\end{align*}
	which is (\ref{eqn: 202}).

@@

Now, recall the matrix-functions
\begin{align*}
	% \bs Q_{+0}(\lambda) &= \bs C_+^{-1}\bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1},
	% %
	% \\\bs Q_{-0}(\lambda) &= \bs C_-^{-1}\bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1},
	%
	\bs Q_{++}(\lambda) &= \bs C_+^{-1} \left(\bs T_{++} - \lambda \bs I + \bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0+}\right),
	%
	\\\bs Q_{+-}(\lambda) &= \bs C_+^{-1} \left(\bs T_{+-} + \bs T_{+0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0-} \right) ,
	%
	\\\bs Q_{--}(\lambda) &= \bs C_-^{-1} \left(\bs T_{--}  - \lambda \bs I + \bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0-}\right),
	%
	\\\bs Q_{-+}(\lambda) &=\bs C_-^{-1} \left(\bs T_{-+}+ \bs T_{-0}\left[\lambda \bs I - \bs T_{00}\right]^{-1}\bs T_{0+}\right) ,
\end{align*}
from Chapter~\ref{sec: conv}.
\begin{cor}\label{cor: mpr B}
	For \(m\in\{+,-\}\) the top-left quadrant of size \(m_1\times m_1=|\calS_m|  p \times |\calS_m|  p\) of \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I_{|\calS_m|  p\times |\calS_m|  p} & \bs 0_{|\calS_m|  p\times |\calS_0|  p}}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t
		\\&\quad{}\times \left[\begin{array}{c} \bs I_{|\calS_m|  p\times |\calS_m|  p} \\ \bs 0_{|\calS_0|  p\times |\calS_m|  p} \end{array}\right], \nonumber
	\end{align}
	is given by 
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm} (\lambda)x}\otimes  e^{\bs S x}\wrt x(\bs C_m^{-1}\otimes \bs I).\label{eqn: skagh87} 
	\end{align}
	For \(m\in\{+,-\}\) the top-right quadrant of size \(m_1\times m_2=|\calS_m|  p\times |\calS_0|  p\) of  \(e^{\bs B_{mm}t}\), 
	\begin{align}
		&\vligne{\bs I_{|\calS_m|  p\times |\calS_m|  p} & \bs 0_{|\calS_m|  p\times |\calS_0|  p}}\int_{t=0}^\infty e^{-\lambda t} \exp\left\{\left[\begin{array}{cc} \bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S & \bs T_{m0}\otimes \bs I \\ \bs T_{0m} \otimes \bs I & \bs T_{00}\otimes \bs I \end{array}\right]t\right\} \wrt t 
		\\&\quad{}\times \left[\begin{array}{c}\bs 0_{|\calS_m|  p\times |\calS_m|  p} \\ \bs I_{|\calS_0|  p\times |\calS_0|  p}\end{array}\right] ,\nonumber
	\end{align}
	is given by
	\begin{align}
		\int_{x=0}^\infty e^{\bs Q_{mm}(\lambda)x}\otimes  e^{\bs S x}\wrt x((\bs C_m^{-1}\bs T_{m0}(\lambda \bs I - \bs T_{00})^{-1})\otimes \bs I).\label{eqn: skagh873} 
	\end{align}
	Also, 
	\begin{align}
		&\vligne{\bs I_{|\calS_m|  p\times |\calS_m|  p} & \bs 0_{|\calS_m|  p\times |\calS_0|  p} }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t \bs{B}_{m{n}} %= \vligne{\bs I & \bs 0 }\int_{t=0}^\infty e^{-\lambda t} e^{\bs{B}_{mm}t} \wrt t  \left[\begin{array}{cc} \bs{T}_{mn}\otimes \bs{D} & \bs 0 \\ \bs T_{0n}\otimes \bs D & \bs 0 \end{array}\right]
		\\&= \int_{x=0}^\infty \bs H^{mn}(\lambda,x)  \otimes  e^{\bs S x}\bs D\wrt x\left(\vligne{\bs I_{|\calS_n|p} & \bs 0_{|\calS_n|p\times |\calS_0|p}}\right), \label{eqn: akgj987adKLDJ}
\end{align}
for \(m,n\in\{+,-\}\), \(m\neq n\).
\end{cor}
\begin{proof}
	From Lemma~\ref{lem: sfkjgn} the top-left quadrant of size \(m_1\times m_1=|\calS_m|  p \times |\calS_m|  p\) of the integral with respect to \(t\) on the left-hand side of (\ref{eqn: skagh87}) is 
	\begin{align}
		\int_{t=0}^\infty e^{\left(\bs T_{mm}\otimes \bs I + \bs C_m\otimes \bs S - \lambda \bs I+ (\bs T_{m0}\otimes \bs I)(\lambda \bs I-\bs T_{00}\otimes \bs I)^{-1}(\bs T_{0m}\otimes \bs I)\right)t}\wrt t. \label{eqn: akjf768}
	\end{align}
	By Lemma~\ref{lem: lst mpr}, (\ref{eqn: akjf768}) is equal to 
	\begin{align}
		&\int_{x=0}^\infty e^{\bs C_m^{-1}\left(\bs T_{mm} - \lambda \bs I+ \bs T_{m0} (\lambda \bs I-\bs T_{00})^{-1}\bs T_{0m} \right)x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1}\nonumber
		%
		\\&=\int_{x=0}^\infty e^{\bs Q_{mm} ( \lambda )x}\otimes e^{\bs Sx}\wrt x(\bs C_m\otimes \bs I)^{-1} , \label{eqn: akjf7623988}
	\end{align}
